### 2016-11-28 intro.tex
intro touch ups

\heading{Case Studies.}
This example offers a hint at the broad range of abstract data structures our syntax supports.  In this paper, we put the syntax and our security notions to work, analyzing Bloom filters in the random oracle model~\cite{broder2004network}, with PRFs for hash functions~\cite{niedermeyer2014cryptanalysis,naor2015bloom}, and with secret hash functions that fall short of being PRFs (so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}), each representing an in-use or proposed Bloom filter variant.  The linear-PRF Bloom filter provides an opportunity to see just how brittle constructions can be to their usage.  When used to create a representation of a set, we prove that the linear-PRF Bloom filter offers both correctness and privacy.  However, when applied to a multiset (effectively) privacy is lost.  In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.  Note that this is despite the fact that the hash functions are constructed from secretly-keyed PRFs in a way that has been suggested in recent literature on Bloom filter variants~\cite{kirsch2006less}.  We also consider garbled Bloom filters, proposed by Dong et al.~\cite{dong2013private} as a key piece of a private set-intersection protocol.

>>>>

\heading{Case Studies.}
This example offers a hint at the broad range of abstract data structures our syntax supports.  In this paper, we put the syntax and our security notions to work in several case studies.  First, we analyze classical Bloom filters when the hash functions are modeled as public random oracles~\cite{broder2004network}, when the hash functions are secretly-keyed PRFs ~\cite{niedermeyer2014cryptanalysis,naor2015bloom}, and when the hash functions are secretly keyed but fall short of being PRFs, i.e., so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}.  Each of these represents an in-use or proposed Bloom filter variant.

The linear-PRF Bloom filter provides an opportunity to see just how brittle constructions can be to their usage.  When used to create a representation of a set, we prove that the linear-PRF Bloom filter offers both correctness and privacy.  However, when applied to a multiset (effectively) privacy is lost.  In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear-PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.  Note that this is despite the fact that the hash functions are constructed from secretly-keyed PRFs in a way that has been suggested in recent literature on Bloom filter variants~\cite{kirsch2006less}.

We also consider garbled Bloom filters, proposed by Dong et al.~\cite{dong2013private} as a key piece of a private set-intersection protocol.
